Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-24 doc/main_jfm.tex
update Fig. 5 and table

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{Slip.eps}
\end{center} 
  \caption{The schematic of the intermonolayer slip over a period of time. Taking shear rate $\chi=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position. The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=\{2000,5200,9000\}$. The midplane curve is denoted as $\Sigma_M$.
  }
    \label{figure5}
\end{figure}

@@

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c c c c c }
 $\chi$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
\hline                    
$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
%$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
%$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
$b$ (pN$\cdot$ns nm$^{-2}$)    & 3.56 & 3.53 & 3.52 & 3.61 & 3.57 & 3.56 & 3.58\\ 
\hline    
\end{tabular} 
\label{table1}
\end{table}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Slip.eps}
\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{The schematic of the intermonolayer slip over a period of time. Taking shear rate $\chi=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position. The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=2000$ and $t=9000$. The midplane curve is denoted as $\Sigma_M$. We provide numerical results of $\theta(t)$ for cases of shear rates.
  }
    \label{figure5}
\end{figure}

@@

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c c c c c }
 $\chi$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
\hline                    
$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
%$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
%$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
$b$ (pN$\cdot$ns nm$^{-2}$)    & 1.38 &  5.43 & 1.37 &  1.33 & 8.07 & 1.94  & 1.89\\ 
\hline    
\end{tabular} 
\label{table1}
\end{table}
